Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-25 paper/paper.tex
rewroded abstract, added urls to repositories

\begin{abstract}
With continual miniaturization ever more applications of deep learning can be found
in embedded systems, where it is common to encounter data with natural complex domain
representation. To this end we extend Variational Dropout to complex-valued neural
networks. We verify the proposed Bayesian technique and assess the performance-compression
trade-off by conducting a large-scale numerical study of $\cplx$-valued networks on
two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
on MusicNet. We reliably replicate the state-of-the-art result by \citet{trabelsi_deep_2017}
for $\cplx$-valued networks on MusicNet with $50-100\times$ compression rate.
\end{abstract}

@@

>>>>

\begin{abstract}
With continual miniaturization ever more applications of deep learning can be found
in embedded systems, where it is common to encounter data with natural complex domain
representation. To this end we extend Sparse Variational Dropout to complex-valued neural
networks and verify the proposed Bayesian technique by conducting a large numerical
study of the performance-compression trade-off of $\cplx$-valued networks on two tasks:
image recognition on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
We replicate the state-of-the-art result by \citet{trabelsi_deep_2017} on MusicNet with
a $\cplx$-valued network compressed $50-100\times$ at a small performance peanlty.
\end{abstract}

@@

Source code for the experiments conducted in this study and figures is available at
\url{https://github.com/ivannz/complex_paper}.
%
Source code for a PyTorch extension which implements $\cplx$-valued Variational Dropout and
ARD layers, and provides basic layers for $\cplx$-valued networks, including maskable
sparsified layers, is available at
\url{https://github.com/ivannz/cplxmodule}.
\smallskip
